### 2013-09-27 Publications/2013-ISBI14/03-methods.tex
Paper ISBI

\paragraph*{Evaluation scores}
In order to assess the geometrical correctness of the
recovered phantoms, we report overlap indices, specifically
the fuzzy Jaccard index as proposed in
\cite{crum_generalized_2006} weighted by the volumes of
labels. The recovered signal \emph{sanity} (dropout 
correction) is evaluated with correlation maps, averaged
along the time axis to take into account all the volumes
existing on the \gls*{dmri} data. This checkpoint
assumes that geometrical distortion is precisely
corrected. Finally, we report the impact on tractography
using the \gls*{frr}, that informs the number of recovered
fibers versus the gold-standard number for a specific
reconstruction method, and the error on the resulting
connectivity matrices.

>>>>

\paragraph*{Evaluation scores}
We evaluated three characteristics of the corrected
phantom. First, we assessed the geometrical correctness
and reported overlap indices of three \glspl*{tpm} 
(namely \gls*{csf},\gls*{wm}, and \gls*{gm}).
More precisely, we computed the \gls*{fji} as 
proposed in \cite{crum_generalized_2006} weighted by 
the volumes of labels. 
Second, to evaluate the quality of the actual 
signal \emph{sanity} after recovery (dropout 
correction), we studied the signal similarity
frame by frame computing the $\ell_1$-norm
based correlation index. We report this score
on the B0 and the average of the remaining 32 
\glspl*{dwi}. Third, we report the 
impact on tractography using the \gls*{frr}, that 
informs the number of recovered fibers versus the 
gold-standard number for a specific reconstruction
method.

### 2013-09-27 Publications/2013-ISBI14/04-results.tex
Paper ISBI

WIP: work in progess..

>>>>

\subsection{Geometrical correctness}

The three methods under study achieved good results in
terms of geometrical accuracy. In this ranking, the best
results were obtained with the \gls*{reb} method. Second
best were obtained with \gls*{t2b}. We visually checked
the numbers reported in \autoref{table:results}. 
\autoref{fig:results} shows the B0 volumes after correction.

\subsection{Signal loss recovery}

A second workflow evaluated the different correction methodologies
with analysis of the outcome similarity with respect to the
the original signal. In this second study, \gls*{reb} performed
significantly better than the other two methods, as reported
in \autoref{table:results}.

\subsection{Tractography impact}

Tractography was shown to be deeply influenced by distortion and
the correction method choice. As expected from the scores obtained
by \gls*{reb} in the signal similarity check, this is also the
best ranked method in this category.

\subsection{Discussion}

\input{041-results-table}

\begin{figure}[thpb]
   \centering
   \includegraphics[width=0.8\columnwidth]{Fig02-Results}
   \caption{Visual results}
   \label{fig:results}
\end{figure}

Even though all the surveyed methods produced visually sound results,
\gls*{reb} showed the best results for all the tests. Therefore,
this study suggests that \gls*{reb} is the best available
methodology for susceptibility-induced distortions in
\gls*{epi}. An important limitation of this work is that 
\gls*{psf}-based methods could not be compared, as a
\gls*{psf} map consistent with the synthetic phase-difference
map could not be generated. Nonetheless, to our knowledge there are
no \gls*{psf}-based methods with readily available implementations
for comparison. Moreover, whereas acquiring one extra dataset
among \gls*{t2}, fieldmap, or reversed-encoding B0 is included in
every typical \gls*{dmri} acquisition protocol, the \gls*{psf} 
mapping is not usually performed. Therefore, the most common
correction methodologies are included in the proposed evaluation
framework, along with the benchmarking results.
